---
title: "Data"
author: "Hunter Snyder"
date: "1/17/2019"
output: html_document
---

#Load in packages
```{r, warning = F, message = F}
library(ggplot2)
library(tidyverse)
library(DT)
```


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


# Data tidying 
Read in Alaska Department of Fish and Game, Division of Commercial Fisheries. 2017. Daily salmon escapement counts from the OceanAK database, Alaska, 1921-2017. Knowledge Network for Biocomplexity. doi:10.5063/F1S46Q6M. 

```{r}
esc <- read.csv(file ="https://knb.ecoinformatics.org/knb/d1/mn/v2/object/urn%3Auuid%3Af119a05b-bbe7-4aea-93c6-85434dcb1c5e", stringsAsFactors = F)

#head(esc)
```
 
 Calculate annual, regional total escapement
 
 separate the data into year month day
 group by and summarize to calculate sum over unqiue regions by year by spp
 filter for salmon species
 
```{r}
annual_esc <- esc %>% 
  separate(sampleDate, into = c("year", "month", "day", sep = "-")) %>% 
  mutate(year = as.numeric(year)) %>% 
  group_by(SASAP.Region, Species, year) %>%
  summarize(escapement = sum(DailyCount)) %>% 
  filter(Species %in% c("Chinook", "Sockeye", "Pink", "Chum", "Coho"))
           
```
```{r}
datatable(annual_esc)
```
 
 
# Create static plots using ggplut 

```{r}
ggplot(annual_esc, aes(x= Species, y = escapement, fill = Species)) + 
  geom_col()
```

```{r}
#kodiak_esc <- annual_esc %>%
 # filter(annual_esc, SASAP.Region == "Kodiak")

ggplot(data = filter(annual_esc, SASAP.Region == "Kodiak"), 
       aes(x = year, y = escapement, color = Species)) +
  geom_line() + 
  #where are the points?
  geom_point() +
  ylab("Escapement (number of fish)") + 
  xlab("Time") + 
  ggtitle("Kodiak Salmon Escapement")
```
 
 
```{r, fig.height= 10, fig.width= 8}
ggplot(annual_esc, aes(x = year, y = escapement, color = Species)) + 
  geom_line() + 
  geom_point() +
  facet_wrap(~SASAP.Region, scales = "free", ncol = 2)

ggsave("region_escapement.png")
```
 
# Interactive Map
 